Compositional equivalences based on Open pNets

### 2021-09-22 2016-Weak-FH-Bisim/WeakBisim.tex
corrected one highlighted dsentence

We define now a bisimulation relation tailored to open automata and their parametric nature. \hl{This relation relates states of the open automaton and states equivalence between the open transitions between the states.!?} Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.

>>>>

We define now a bisimulation relation tailored to open automata and their parametric nature. This relation relates states of the open automaton and guarantees that the related states are observationally equivalent, i.e. equivalent states can trigger transitions with identical action labels. Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.
